---
title: "lab3"
author: "Xinhao Li"
date: "June 9, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Importing the Data
Run install the package `readr` by running `install.packages("readr")` in the console.

The code below reads in the `tents.csv` comma-separated file.  The `col_types` argument is telling `R` what the data type is in each column.  See `?read_csv` if you're curious.
```{r}
library(readr)
tents <- read_csv("tents.csv", col_types = "ccnniccc")
```

### Questions
Answer the following questions programatically.  Some questions ask for you to explain what you see---you may answer this as text outside a code block.

1. Run `str()` on `tents`.  What information does it tell you? This is a useful function to know.
```{r}
str(tents)
```
This function gives a structure of tents like summary. It shows what the class is and what the type each rows are.   
2. What class is `tents`?  
The class is ‘tbl_df’, ‘tbl’ and 'data.frame'  
3. How many rows are in `tents`?  
There are 90 rows.  
4. How many columns are in `tents`?  
There are 8 rows.  
5. What are the names of the columns?  
The names of the columns are `r names(tents)`.  
6. Display the first 5 rows.
```{r}
head(tents,5)
```

7. Display the last 4 rows.  
```{r}
tail(tents,4)
```
8. Find out how to use `quantile` to find the interquartile range (75th percentile - 50th percentile) of the weights of the tents.  
```{r}
temp = quantile(tents$weight)
temp[['75%']] - temp[['25%']]
```
The the interquartile range (75th percentile - 50th percentile) of the weights of the tents is `r temp[['75%']] - temp[['25%']]`  
9. Find the standard deviation of the heights of the `tents`.  Does `R` use `n` or `n-1` in the denominator when calculating standard deviation?  
```{r}
sd(tents$height)
```
The standard deviation of the heights of the `tents` is `r sd(tents$height)`. `R` use `n-1` in the denominator when calculating standard deviation.  
10. The weight is given in grams.  Add a new column to the data frame called `weight_lbs` that contains the weight of the tents in pounds.  Remember to overwrite `tents` with your update.  
```{r}
tents$weight_lbs = tents$weight/453.59237
tents$weight_lbs
```

11. The height is given in centimeters.  Add a new variable `height_in` to the data frame that contains the height of the tents in inches. Remember to overwrite `tents` with your update.  
```{r}
tents$height_in = tents$height*0.393701
tents$height_in
```

12. How many tents cost more than $400?  
There are `r length(tents$price[which(tents$price>400)])` tents cost more than $400.  
13. Subset the data frame so that it only contains tents that are valued $300 or less.  Assign the subsetted data frame the name `so_cheap_tents`.  
```{r}
so_cheap_tents = subset(tents,price<=300)
so_cheap_tents
```

14. Of the tents that are more than $300, what percent are `big-agnes` tents?  
The percent are `big-agnes` tents that are more than $300 is `r nrow(subset(tents,price>300 & brand == 'big-agnes'))/length(tents$price[which(tents$price>300)])`

15. Select the `bestuse` column of `tents` in four different ways: using `$`, `[[]]`, position number and `[]`, and variable name and `[]`.  
```{r, eval=F}
tents$bestuse
tents[["bestuse"]]
tents[6]
tents["bestuse"]
```

16. What is the name of the tents with the best height-to-weight ratio?  
```{r}
tents$height_to_weight = tents$height/tents$weight
```

The name of the tents with the best height-to-weight ratio is `r tents$name[which.max(tents$height_to_weight)]`  
17. Run `table` with two arguments, `seasons` and `capacity` (this should be one table).  What did it do?  
```{r}
table(tents$seasons,tents$capacity)
```
This function uses the cross-classifying factors between `seasons` and `capacity` to build a contingency table of the counts at each combination of them.  
18. What type of tent (bestuse) is the most common? Your answer should return only the use and not the count.  
The most common type of tent is `r names(which.max(table(tents$bestuse)))`.  
19. Create a data frame called `kelty` with only data on kelty tents.  Do the same for `big-agnes`.  Then, combine the two data frames.  
```{r}
kelty = subset(tents,brand =='kelty')
big_agnes = subset(tents,brand =='big-agnes')
rbind(kelty,big_agnes)
```

