---
title: "lab6"
author: "Xinhao Li"
date: "June 15, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Importing packages
```{r}
library(stringr)
```

## Population Variance

Write a function `MyVar` that calculates the population variance of a vector.  If you need a refresher of what that means, [this section of wikipedia should help](https://en.wikipedia.org/wiki/Variance#Population_variance_and_sample_variance).
```{r}
MyVar <- function(x){
  return((1/length(x))*(sum((x-mean(x))^2)))
}
```


## Finding Roots
Write a function `zeroes` that finds the roots (zeroes) of a degree two polynomial.  The function should take the coefficients of the polynomial $a^2x + bx + c$ as its arguments and returns a vector of roots.  If there are no real roots, the function should stop and produce an error message: `"This polynomial has no real roots."`  
My function:
```{r}
zeroes <-function(a,b,c){
  delta = b^2 - 4*a*c
  if (delta < 0){
    stop("This polynomial has no real roots.")
  } else {
    (-b+sqrt(delta))/2/a
    return(c((-b+sqrt(delta))/2/a,(-b-sqrt(delta))/2/a))
  }
}
```

Test your function:
```{r, eval = F}
zeroes(1, 0, 0)
zeroes(1, 0, 1)
zeroes(1, 1, 1)
```

## Temperature Conversion

Write a function `ConvertTemperature` that takes a numeric vector of temperatures in Fahrenheit and converts them into Celsius, Kelvin, Rankine, Delisle, Newton, Reamur, or Romer, depending on what the user specifies in an argument called `to`.  If they specify some other temperature scale, return the message "The [their input] temperature scale is not supported".  If you don't know the conversions, (see this table)[https://en.wikipedia.org/wiki/Conversion_of_units_of_temperature#Fahrenheit]
My function:
```{r}
ConvertTemperature <- function(t,to){
  if (to == "Celsius"){
    return((t-32)*5/9)
  } else if (to == "Kelvin"){
    return((t+459.67)*5/9)
  } else if (to == "Rankine"){
    return(t+459.67)
  } else if (to == "Delisle"){
    return((212-t)*5/6)
  } else if (to == "Newton"){
    return((t-32)*11/60)
  } else if (to == "Reamur"){
    return((t-32)*4/9)
  } else if (to == "Romer"){
    return((t-32)*7/24+7.5)
  } else{
    stop(str_c('The ',to,' temperature scale is not supported'))
  }
  
}
```

Test your function
```{r, eval = F}
ConvertTemperature(32, "Celsius") == 0
ConvertTemperature(212, "Kelvin") == 373.15
ConvertTemperature(10, "Rankine") == 501.67
```


## Rolling Dice

For this problem, you'll need the `sample` and `pmax` function.  `sample` generates a random sample of a specified size either with or without replacement.  You can specify probability weights for each element of your sample space using the `prob` argument.  By default, each element will have equal probability.
```
sample(x = vector_to_be_sampled, size, replace = FALSE, prob = NULL)
```
1. What does `pmax` do? How is it different from `max`? Hint: test both on the two vectors `c(1, 5, 3)` and `c(2, 4, 2)`.  
```{r}
max(c(1,5,3),c(2,4,2))
pmax(c(1,5,3),c(2,4,2))
```
`pmax` can take one or more vecotrs as arguments and return a single vecotr giving the 'parallel' maxima of the vectors. The `max` only return the global maximum.  
2. When you "roll dice with advantage", you roll a pair of dice and take the higher value as your roll.  Write a function `AdvRoll` the simulates rolling with advantage `n` times. The function should take on 2 arguments `sides` and `n` and output a length `n` vector of rolls.  
```{r}
AdvRoll <- function(sides,n){
  a = sample(sides,n,replace=T)
  b = sample(sides,n,replace=T)
  return(pmax(a,b))
}
```

3. Write your own summary function called `MySummary` that, given a numeric vector `x`, returns the following summary statistics: mean, median, mode, sum, and sum of squares.
```{r}
MySummary<-function(x){
  return(list(mean=mean(x),median=median(x),mode=names(which.max(table(x))),sum=sum(x),sum_of_squares=sum(x^2)))
}
```

4. Using your two functions, simulate "rolling dice with advantage" 1000 times and find the summary statistics.
```{r}
MySummary(AdvRoll(6,1000))
```

